\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry} 
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage{titlesec}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{array}
\usepackage{booktabs}
\usepackage{ragged2e}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{cleveref}
\usepackage{slashed}
\usepackage{commath}
\usepackage{lipsum}
\usepackage{colonequals}
\usepackage{addfont}
\usepackage{enumitem}
\usepackage{sectsty}

\subsectionfont{\itshape}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\let\oldproofname=\proofname
\renewcommand{\proofname}{\bf{\textit{\oldproofname}}}

\theoremstyle{definition}
\newtheorem{example}{Example}[section]

\newtheorem*{discussion}{Discussion}



\begin{document}

\title{\textbf{Mathematics Symposium}}
\author{House of Hits}
\date{25 May 2019}
\maketitle

\section{Description}

 We welcome you to join us on May $25^{th}$ at 3:00PM in the lobby at the House of Hits. What this will be is a presentation on an interesting topic from math followed by a discussion amongst all those in attendance. This event is open for the general public and is free of charge. We hope to make this as interactive and engaging as possible. This means that during and after the presentation any and all questions are welcome. 

\subsection{Topics to be Discussed}

\begin{itemize}
    \item Introduction to Formal Proofs
    \item Propositional Logic
    \item The Axioms of Set Theory
    \item Introduction to The Real Numbers
    \item Introduction to Group Theory
    \item Introduction to Wave Mechanics (Applications to Music)
\end{itemize}

\noindent Finally, we would also like to incorporate how math can be used to answer questions from the world around us. Thus, come prepared with questions (any kind!), and during the discussion we will try to formalize the question and see if we can answer it. This process of exploration often leads to beautiful discovery, so let us explore!

\vspace{12mm}

\centerline{\Large{So Join Us In Our Debut Mathematics Symposium!}}

\vspace{10mm}

\centerline{\large{Oh! And Free Pizza!}}

\end{document}